quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-04-05 paper-quollr.Rmd
Found the best layout

nldr5 <- pacmap_limb |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  interior_annotation("e")
```

@@

error_limb <- bind_rows(error_limb_umap, 
                        error_limb_tsne,
                        error_limb_phate,
                        error_limb_trimap,
                        error_limb_pacmap)

error_limb <- error_limb |>
  mutate(a1 = round(a1, 2)) |>
  filter(bin1 >= 5) |>
  group_by(method, a1) |>
  filter(MSE == min(MSE)) |>
  ungroup()

error_limb <- error_limb |>
  mutate(method = factor(method,
                         levels = c("UMAP_15_min_dist_0.1","tsne_30", "phate_5", "trimap_n-inliers_12_n-outliers_4_n-random_3", "pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2")))
```

@@

free(error_plot_limb) + wrap_plots(
  nldr1, nldr2, nldr3, 
  nldr4, nldr5, ncol = 2)
```

>>>>

nldr5 <- pacmap_limb |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  interior_annotation("e")

tsne_limb2 <- read_rds("data/limb_muscles/facs_limb_muscles_tsne_perplexity_15.rds")

nldr6 <- tsne_limb2 |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  interior_annotation("f")
```

@@

error_limb_tsne2 <- read_rds("data/limb_muscles/error_limb_muscles_tsne_perplexity_15.rds")

error_limb <- bind_rows(error_limb_umap, 
                        error_limb_tsne,
                        error_limb_phate,
                        error_limb_trimap,
                        error_limb_pacmap,
                        error_limb_tsne2)

error_limb <- error_limb |>
  mutate(a1 = round(a1, 2)) |>
  filter(bin1 >= 5) |>
  filter(a1 >= 0.03) |>
  group_by(method, a1) |>
  filter(MSE == min(MSE)) |>
  ungroup()

error_limb <- error_limb |>
  mutate(method = factor(method,
                         levels = c("UMAP_15_min_dist_0.1","tsne_30", "phate_5", "trimap_n-inliers_12_n-outliers_4_n-random_3", "pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2", "tsne_15")))
```

@@

free(error_plot_limb) + wrap_plots(
  nldr1, nldr2, nldr3, 
  nldr4, nldr5, nldr6, ncol = 2)
```
